Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-29 thesis/chapters/ch_chapter4.tex
More writing

To frame this analysis, lets first examine what processes affect the metal mass fraction PDF. The mean metal mass fraction for a collection of gas is simply the total metal mass divided by the total gas mass. For a collection of gas elements, the mean metal mass fraction is defined as $Z_{\rm gas} = \frac{ \Sigma Z_{\rm i}M_{\rm gas,i}}{\Sigma M_{\rm gas,i}}$, where $M_{\rm gas,i}$ is the mass of the i$^{\rm th}$ homogeneous blob of gas, and $Z_{i}$ its metal mass fraction. A completely homogenous ISM would have a $\delta$ function metal mass fraction PDF at the mean metal fraction, or $p(Z) = \delta(Z_{\rm gas})$. By definition, a completely homogeneous distribution will have

>>>>

To frame this analysis, lets first examine what processes affect the metal mass fraction PDF. The mean metal mass fraction for a collection of gas is simply the total metal mass divided by the total gas mass. For a collection of gas elements, the mean metal mass fraction is defined as $Z_{\rm gas} = \frac{ \Sigma Z_{\rm i}M_{\rm gas,i}}{\Sigma M_{\rm gas,i}}$, where $M_{\rm gas,i}$ is the mass of the i$^{\rm th}$ homogeneous blob of gas, and $Z_{i}$ its metal mass fraction. A completely homogeneous ISM would have a $\delta$ function metal mass fraction PDF at the mean metal fraction, or $p(Z) = \delta(Z_{\rm gas})$. By definition, then, a homogeneous distribution will have a zero-width IQR, IDR, and mean-median difference. Non-uniform enrichment in a homogeneous medium will increase each of these quantities, while mixing in a non-uniform medium will tend to decrease each. In simple models of galactic chemical evolution, the mean gas abundance -- not the median -- is followed, even though the median is more indicative of the abundance of a ``typical" gas element. Because these two quantities provide a more immediate conceptual understanding of how metals are distributed in the ISM, we focus on characterizing the inhomogeneity of the followed metals by examining the mean-median difference. Though this quantity being zero is necessary for metals to be homogeneously distributed in a medium, we do note that it is not a sufficient condition. However, as noted, its evolution is easy to interpret conceptually. Enrichment increases this quantity by raising the mean metal fraction while keeping the median value fixed (or only slightly increasing), so long as the newly enriched mass is a small fraction of the total gas mass (as is usually the case). Conversely, preferential removal of metals from a medium will lower this quantity. And finally, the mixing of metal-rich gas elements with metal-poor will gradually bring the mean and median values to parity. For our numerical experiments, enrichment in the whole ISM only occurs once, while ejection from the ISM is easy to follow. This allows for a more clean interpretation of the evolution than examining either the IQR or the IDR.

\begin{figure*}
  \centering
  \includegraphics[width=0.75\linewidth]{figures/ch4/ISM_CNM_average_mean-median}
  \caption{Time evolution of the difference (in dex) between the mean metal mass fraction of each source and the median metal mass fraction of each source in all of the gas in the ISM (left) and in the CNM only (right).}
  \label{ch4:fig:CGM_CNM}
\end{figure*}

In Figure~\ref{ch4:fig:mean-median} we examine the average behavior of the mean-median metal mass fractions for the whole ISM in each run (left) and the CNM only (right). In all cases, enrichment drives the dramatic increase of this value from zero to over 10 dex. This large value is due entirely because the initial abundance for each metal is zero. This is followed by a significant decrease in spread over he first 25~Myr or so as metals are preferentially ejected from the ISM via outflows. The delay in this spike in the CNM (compared to the galaxy as a whole) is due to the different timescales over which most of the metals are incorporated into the cold gas, as shown in Figure~\ref{ch4:fig:ISM_CGM}.

Clearly, at no point can any of these distributions be considered well-mixed within the 150~Myr simulation time. \textit{Need to fix up: This is in agreement with the understanding that the mxiing timescales should correspond to XXX, which suggests that it would take $\sim$X~Gyr (1 Gyr?) for the metals to be fully mixed}. Interestingly, however, the injection energy for a given sources leaves an indelible impact on the subsequent evolution of those metals in the ISM throughout the simulation time. We demonstrate that variations in abundance spread across elements may be driven significantly by the enrichment site and its associated $E_{\rm ej}$. Metals from II\_E46 are significantly less well-mixed than their higher-energy counterparts at II\_E51 and II\_E52. Interestingly, II\_E49 behaves much more similarly to II\_E46 -- with poor mixing -- even though it is much closer in energy to the II\_E51. For what mixing does occur in the CNM for these elements, it is apparent that it happens much faster ($\sim$20~Myr) for the highest energy event than the lower energy events which take longer to plateau to a consistent value.

We note that these results are given for \textit{single} enrichment events. If many events occur throughout the galaxy with similar metal yields then this would tend to decrease the abundance variations across the galaxy. However, the AGB wind metals examined in Chapter~\ref{ch:chapter3} are still more heterogeneously distributed than core collapse SNe elements in spite of the fact that these events are both more common than SNe and are more evenly distributed throughout the galaxy.

What this does suggest, however, is that in utilizing stars with unusual abundances at low metallicities to infer the yields of exotic enrichment sources, the spread of abundances in those stars may provide an important insight into the origin of those metals. For example, r-process enrichment from exotic enrichment events like hypernovae should manifest itself as more well-mixed than if the elements originated in lower energy NS-NS mergers.
\textbf{Go back to reticulum papers and see what the spreads on these are}

\section{Discussion}

Not sure how much to put in here, and may very well need to just pull out some of the above and put it here.
